The Cluster Difference Imaging Photometric Survey (CDIPS). I. Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-06-23 paper/ms.tex

\paragraph{Pre-{\it Gaia} OC memberships}
\citet{Kharchenko_et_al_2013} used proper motions calculated in PPMXL
\citep[][a combination of USNO-B1{.}0 and 2MASS
astrometry]{roeser_ppmxl_2010} and near-infrared photometry from 2MASS
\citep{skrutskie_tmass_2006} to report the existence of 2859 open
clusters and stellar associations.
We selected their ``$1\sigma$'' members according to the
combined photometric, kinematic, and spatial criteria described by
\citet{kharchenko_global_2012}.  Then, to obtain {\it Gaia}-DR2 source
identifiers for the members, we performed a crossmatch for {\it
Gaia}-DR2 sources within 5 arcseconds of the listed positions.  As an
additional constraint, we used the 2MASS photometry to predict the
$G$-band magnitudes\footnote{See
\url{https://gea.esac.esa.int/archive/documentation/GDR2/Data_processing/chap_cu5pho/sec_cu5pho_calibr/ssec_cu5pho_PhotTransf.html},
online, \texttt{2019-03-29}, or \citet{carrasco_gaia_2016}}, and
required that the measured $G$-magnitude fall within 2 magnitudes of
the predicted $G$-magnitude.  If multiple neighbors matched the
position and magnitude constraints, we took the nearest spatial
neighbor as the match.  From 373{,}226 stars, this yielded a unique
best neighbor for 352{,}332 stars (94.4\% of the sample), and a choice
between two neighbors for 17{,}774 stars.

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{star_catalog_mag_histogram_phot_rp_mean_mag.png}
	\end{center}
	\vspace{-0.2cm}
	\caption{
    {\bf Cumulative counts of candidate cluster member stars a
    function of Gaia $Rp$-band magnitude.}
	\label{fig:cdips_targets}
	}
\end{figure}

>>>>

\paragraph{Pre-{\it Gaia} OC memberships}
\citet{Kharchenko_et_al_2013} used proper motions calculated in PPMXL
\citep[][a combination of USNO-B1{.}0 and 2MASS
astrometry]{roeser_ppmxl_2010} and near-infrared photometry from 2MASS
\citep{skrutskie_tmass_2006} to report the existence of 2859 open
clusters and stellar associations (globular clusters were
omitted by excluding any entry of type \texttt{'g'}).
We selected ``$1\sigma$'' members according to the
combined photometric, kinematic, and spatial criteria described by
\citet{kharchenko_global_2012}.  Then, to obtain {\it Gaia}-DR2 source
identifiers for the members, we performed a crossmatch for {\it
Gaia}-DR2 sources within 5 arcseconds of the listed positions.  As an
additional constraint, we used the 2MASS photometry to predict the
$G$-band magnitudes\footnote{See
\url{https://gea.esac.esa.int/archive/documentation/GDR2/Data_processing/chap_cu5pho/sec_cu5pho_calibr/ssec_cu5pho_PhotTransf.html},
online, \texttt{2019-03-29}, or \citet{carrasco_gaia_2016}}, and
required that the measured $G$-magnitude fall within 2 magnitudes of
the predicted $G$-magnitude.  If multiple neighbors matched the
position and magnitude constraints, we took the nearest spatial
neighbor as the match.  From 373{,}226 stars, this yielded a unique
best neighbor for 352{,}332 stars (94.4\% of the sample), and a choice
between two neighbors for 17{,}774 stars.

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.45\textwidth]{target_star_cumulative_counts.png}
	\end{center}
	\vspace{-0.2cm}
	\caption{
    {\bf Cumulative number of target stars as
    a function of Gaia $Rp$-band magnitude.}  The selected stars are eiher candidate
    members of clusters, or else have other youth indicators. We only consider stars
    with $G_{\rm Rp} < 16$.
	\label{fig:cdips_targets}
	}
\end{figure}
